Shapes analysis for time series.

### 2024-10-23 NEURIPS24/appendix.tex
update

    Let $\bar{f}\in \rmC^0(\Rset^{d+1},\Rset^d)$, $\bar{\gamma}\in  \mcd(\Rset) $ and $\mathbf{s}_0\in \rmC^0(\msi,\Rset^d)$ with $\msi$ an interval of $\Rset$.
    We have :
    \begin{align}
      \Pi_{\gamma,f}.\msg(\mathbf{s}_0)&=\{(\gamma(t),f(t,\mathbf{s}_0(t))),\eqsp t\in \msi \} \\
      &\label{eq:proof1_last_eq}=\{(t,f\left(\gamma^{-1}(t),\mathbf{s}_0(\gamma^{-1}(t))\right),\eqsp t\in \gamma(\msi) \} \eqsp .
    \end{align}
    By defining $\bar{s}:t\in \gamma(\msi)\to f\left(\gamma^{-1}(t),\mathbf{s}_0(\gamma^{-1}(t))\right) $, we have $\bar{s}\in \rmC^0(\gamma(\msi), \Rset^d) $ by composition of continuous functions
    and $ \msg(\bar{s})= \Pi_{\gamma,f}.\msg(\mathbf{s}_0)$ by \eqref{eq:proof1_last_eq}, which concludes the proof.
\end{proof}
\begin{lemma}
  If we denote by $\msv$ the RKHS associated with the kernel $K_{\msg}$, then for any vector field $v$ generated by \eqref{eq:integration} with $v_0$ satisfying \eqref{eq:def_v0},
   there exist $\gamma \in \msd(\Rset) $ and $f\in \rmC^1(\Rset^{d+1},\Rset^d)$ such that $\phi^v=\Psi_\gamma\circ\Phi_f $.
\end{lemma}
\begin{proof}
  Let $v$ be a vector field generated by \eqref{eq:integration} with $v_0$ satisfying \eqref{eq:def_v0}.
 We remark that the first coordinate of the velocity field $v_\tau$ denoted by $v_\tau^{\text{time}}$ only depends on the time variable $t$ for any $\tau\in[0,1]$.
 Thus, when computing the first coordinate of the deformation $\phi^v$, denoted by $\gamma$, we integrate \eqref{eq:LDDMM_dynamic} with $v_\tau$ replaced by $v_\tau^{\text{time}}$,
  thus $\gamma$ is independant of the variable $x$. Moreover, $\gamma\in \mcd(\Rset)$ since a Gaussian kernel induced an Hilbert space $\msv$ satisfying $|f|_V\leq |f|_\infty+ |\dd f|_\infty  $ for any $f\in \msv$ by \citep[Theorem 9]{glaunes2005transport}.
  For the same reason, we have $\phi^v\in \mcd(\Rset^{d+1})$, and thus its last coordinates denoted by $f$ belongs to $\rmC^1(\Rset^{d+1},\Rset^d)$, and by construction $\phi^v=\Psi_\gamma\circ\Phi_f $.
\end{proof}

>>>>

    Let $\bar{f}\in \rmC^1(\Rset^{d+1},\Rset^d)$, $\bar{\gamma}\in  \mcd(\Rset) $ and $\mathbf{s}_0\in \rmC^1(\msi,\Rset^d)$ with $\msi$ an interval of $\Rset$.
    We have :
    \begin{align}
      \Pi_{\gamma,f}.\msg(\mathbf{s}_0)&=\{(\gamma(t),f(t,\mathbf{s}_0(t))),\eqsp t\in \msi \} \\
      &\label{eq:proof1_last_eq}=\{(t,f\left(\gamma^{-1}(t),\mathbf{s}_0(\gamma^{-1}(t))\right),\eqsp t\in \gamma(\msi) \} \eqsp .
    \end{align}
    By defining $\bar{s}:t\in \gamma(\msi)\to f\left(\gamma^{-1}(t),\mathbf{s}_0(\gamma^{-1}(t))\right) $, we have $\bar{s}\in \rmC^1(\gamma(\msi), \Rset^d) $ by composition of $C^1$ functions
    and $ \msg(\bar{s})= \Pi_{\gamma,f}.\msg(\mathbf{s}_0)$ by \eqref{eq:proof1_last_eq}, which concludes the proof.
\end{proof}
\begin{lemma}
  If we denote by $\msv$ the RKHS associated with the kernel $K_{\msg}$, then for any vector field $v$ generated by \eqref{eq:integration} with $v_0$ satisfying \eqref{eq:def_v0},
   there exist $\gamma \in \msd(\Rset) $ and $f\in \rmC^1(\Rset^{d+1},\Rset^d)$ such that $\phi^v=\Psi_\gamma\circ\Phi_f $.
\end{lemma}
\begin{proof}
  Let $v$ be a vector field generated by \eqref{eq:integration} with $v_0$ satisfying \eqref{eq:def_v0}.
 We remark that the first coordinate of the velocity field $v_\tau$ denoted by $v_\tau^{\text{time}}$ only depends on the time variable $t$ for any $\tau\in[0,1]$.
 Thus, when computing the first coordinate of the deformation $\phi^v$, denoted by $\gamma$, we integrate \eqref{eq:LDDMM_dynamic} with $v_\tau$ replaced by $v_\tau^{\text{time}}$,
  thus $\gamma$ is independant of the variable $x$. Moreover, $\gamma\in \mcd(\Rset)$ since a Gaussian kernel induced an Hilbert space $\msv$ satisfying $|f|_V\leq |f|_\infty+ |\dd f|_\infty  $ for any $f\in \msv$ by \citep[Theorem 9]{glaunes2005transport}.
  For the same reason, we have $\phi^v\in \mcd(\Rset^{d+1})$, and thus its last coordinates denoted by $f$ belongs to $\rmC^1(\Rset^{d+1},\Rset^d)$, and by construction $\phi^v=\Psi_\gamma\circ\Phi_f $.
\end{proof}
